From physical assumptions to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics

### 2017-02-22 2015CompleteDerivation/completeDerivation.tex
Changing title

\title{From physical principles to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics}
\author{Gabriele Carcassi, Christine A. Aidala, David J. Baker, Lydia Bieri}

@@

\ifjournal
	% As the page margins are so large, the full title does not fit
	\titlerunning{From physical principles to classical and quantum particle mechanics}
\fi

>>>>

\title{From physical assumptions to classical and quantum \\ Hamiltonian and Lagrangian particle mechanics}
\author{Gabriele Carcassi, Christine A. Aidala, David J. Baker, Lydia Bieri}

@@

\ifjournal
	% As the page margins are so large, the full title does not fit
	\titlerunning{From physical assumptions to classical and quantum particle mechanics}
\fi
